\section{Related Work}
\label{sec:related}

\Syndicate\ adds to a growing body of work on leveraging existing
storage systems, where the main contributions are in separating storage 
concerns into independent components, and applying the end-to-end
principle~\cite{end-to-end} to move storage features to application end-points.
Separating consistency has been exploited
to provide causal consistency~\cite{bolt-on-causal-consistency},
ACID semantics~\cite{deuteronomy}, and key-group transactions~\cite{g-store,scatter} on
top of unmodified cloud storage.  Separating access and admission control 
has been achieved with Kerberos~\cite{kerberos}, and is
exploited today in Web applications with federated identity 
management~\cite{openid,oauth,shibboleth} for single sign-on.
Cloud storage customers enforce storage policies transparently using
{\it cloud storage gateways}---on-site middleboxes that apply the policies
locally (examples include~\cite{riverbed-gateway, amazon-gateway, twinstrata-gateway}).
Customers can also mount certain cloud storage as filesystems~\cite{dropbox,s3fs},
and then layer special-purpose filesystems on top of them that apply 
storage policies transparently (such as encryption~\cite{encfs}).

Unlike prior work, \Syndicate\ separates all of these concerns in a coherent manner.
By applying our consistency protocol to both data and control plane information.
we leverage edge caches to distribute object data, process
certificates, and install end-point functionality in a scalable, secure way.

Many peer-to-peer storage systems~\cite{oceanstore,bayou,practi,kademlia,chord,pastry,dot},
caching systems~\cite{sloppy-dht,karger99,akamai,breslau99},
and distributed filesystems~\cite{afs,xFS,ceph,wheelfs,farsite,tahoe-lafs,shark,ivy}
have preceded \Syndicate, and address consistency, security, and storage policy
in different contexts while offering similar feature sets.
\Syndicate\ differs from these systems in two ways:  its
approach to systems building, and how it leverages caches.  Whereas prior works focus on
combining resource-constrained hosts to form scalable storage
systems, \Syndicate\ focuses on a general way of combining
scalable storage systems into virtual
storage systems for cloud-hosted applications.
Whereas prior works relied on system-specific caches and used client/cache polling,
object leases, and cache invalidation protocols (such as~\cite{wcdp,Gwertzman96,Liu97,gray89})
to scalably deliver consistent data to readers (if they used them at all), \Syndicate\
exploits already-deployed, unmodified Web caches to obtain a scalable data and control plane.
In doing so, \Syndicate\ complements prior and future caching and storage systems by
letting applications use any of them transparently as underlying providers.

Web thin clients (such as~\cite{chromeos}) combine
local and cloud storage to reduce operating costs.  However, they are vertically integrated,
making it difficult to use infrastructure beyond what the vender supports.