\section{Related Work}

Since inception of SMTP little had been done with respect to mail transport protocol. Most of these works argue that design of SMTP incentivize SPAM as it gives no control over receiver to what he gets in his inbox. It has also been argued that in general push based architectures/protocols have a higher tendency to attract unwanted traffic\cite{PushVsPull}. Therefore these works suggest a pull based approach to email instead of the push based approach used by SMTP. 

DMTP (Differentiated Message Delivery Protocol) \cite{dtmp} is a protocol that forces sender to store email in his own storage before recipient reads it into his inbox unless the sender is known in advance. Only emails sent by senders knowns to the recipient will be stored in recipient's mail box. Due to this approach DMTP eliminates economies of scale and increases accountability of SPAM.

In 2000 Internet Mail 2000 \cite{im2k} was proposed by Daniel J. Bernstein, which shifts the responsibility of mail storage from recipient to sender through a pull based approach that replaces SMTP which is analogous to conventional smail mail. Original IM 2000 proposal does not specify mechanisms such as how recipients should be notified, how messages should be downloaded etc. StubMail \cite{stubmail} is an implementation of IM 2000, with StubMail sender uploads the email to a permanently connected outbox (storage) and sends a UDP notification to the recipient’s mail service provider as an RSS feed. Similar to DMTP this implementation also shifts storage responsibility from recipient to sender discouraging SPAMers. StubMail uses either HTTP or SMTP to upload mail to the outgoing storage, message notifications were sent over UDP to eliminate possibility of DoS attacks that could happen with TCP. HTMP (Hypertext Mail Protocol)\cite{htmp} too is based on IM 2000 and uses HTTP as a transport utilizing its’ PUT, GET and DELETE methods to handle email. In all of these designs email addresses of the sender and the receiver have to be exchanged out of band since receiver cannot receive emails if receiver does not know the location of sender’s mail OutBox.

However none of these designs were adopted as a main stream email protocol, this could have been largely due to wide adoption of SMTP and availability of free webmail services. At the time of inception there was no incentive in pushing storage responsibility to end - user when free webmail systems were readily available with Gigabytes of storage. However during the last few years webmail users have become more conscious about privacy and fully aware of the fact that free storage comes at the cost of either being spied by the government or becoming a target of an advertising campaign. On the other hand high availability online storages systems have become feasible enough for individual users through cloud storage services like Amazon, Dropbox etc. Therefore current technology and circumstances calls for a new mail transfer protocol that follows IM 2000 but accompanying novel mechanisms with respect to storage and privacy. In addition users are also keen on having full control over their content stored in the cloud storage and ability to move their data across different cloud storage providers. On the other hand by allowing users to plug-in their own cloud storage webmail services can liberate themselves from the burden of developing and maintaining high performance backend storage systems optimized for serving email.

